---
title: "Calculate Interval Lengths"
author: "Jonathan Boss"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### MESSI Data Example

95% confidence Intervals for the NDE (Visit 1, Cytochrome p450 Pathway):

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)

setwd("/filepath/")

load("protect_output_cytochromep450_param_boot.Rdata")

summary.table <- rbind(subset(mbp.v1.out[[1]], param == "NDE"),
                       subset(mibp.v1.out[[1]], param == "NDE"),
                       subset(mbzp.v1.out[[1]], param == "NDE"))
summary.table$method <- "Unconstrained"

save.table <- summary.table

summary.table <- rbind(subset(mbp.v1.out[[2]], param == "NDE"),
                       subset(mibp.v1.out[[2]], param == "NDE"),
                       subset(mbzp.v1.out[[2]], param == "NDE"))
summary.table$method <- "MESSI (EB)"

save.table <- rbind(save.table, summary.table)

summary.table <- rbind(subset(mbp.v1.out[[3]], param == "NDE"),
                       subset(mibp.v1.out[[3]], param == "NDE"),
                       subset(mbzp.v1.out[[3]], param == "NDE"))
summary.table$method <- "Discrete Selection"

save.table <- rbind(save.table, summary.table)

summary.table <- rbind(subset(mbp.v1.out[[4]], param == "NDE"),
                       subset(mibp.v1.out[[4]], param == "NDE"),
                       subset(mbzp.v1.out[[4]], param == "NDE"))
summary.table$method <- "Hard Constraint"

save.table <- rbind(save.table, summary.table)
save.table$param <- "DE"
save.table$int.length <- save.table$ucl95 - save.table$lcl95

knitr::kable(save.table %>% filter(met.nm == "MBP"), digits = 3)

knitr::kable(save.table %>% filter(met.nm == "MIBP"), digits = 3)

knitr::kable(save.table %>% filter(met.nm == "MBZP"), digits = 3)
```

95% confidence Intervals for the NIE (Visit 1, Cytochrome p450 Pathway):

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)

setwd("/filepath/")

load("protect_output_cytochromep450_param_boot.Rdata")

summary.table <- rbind(subset(mbp.v1.out[[1]], param == "NIE"),
                       subset(mibp.v1.out[[1]], param == "NIE"),
                       subset(mbzp.v1.out[[1]], param == "NIE"))
summary.table$method <- "Unconstrained"

save.table <- summary.table

summary.table <- rbind(subset(mbp.v1.out[[2]], param == "NIE"),
                       subset(mibp.v1.out[[2]], param == "NIE"),
                       subset(mbzp.v1.out[[2]], param == "NIE"))
summary.table$method <- "MESSI (EB)"

save.table <- rbind(save.table, summary.table)

summary.table <- rbind(subset(mbp.v1.out[[3]], param == "NIE"),
                       subset(mibp.v1.out[[3]], param == "NIE"),
                       subset(mbzp.v1.out[[3]], param == "NIE"))
summary.table$method <- "Discrete Selection"

save.table <- rbind(save.table, summary.table)

summary.table <- rbind(subset(mbp.v1.out[[4]], param == "NIE"),
                       subset(mibp.v1.out[[4]], param == "NIE"),
                       subset(mbzp.v1.out[[4]], param == "NIE"))
summary.table$method <- "Hard Constraint"

save.table <- rbind(save.table, summary.table)
save.table$param <- "IE"
save.table$int.length <- save.table$ucl95 - save.table$lcl95

knitr::kable(save.table %>% filter(met.nm == "MBP"), digits = 3)

knitr::kable(save.table %>% filter(met.nm == "MIBP"), digits = 3)

knitr::kable(save.table %>% filter(met.nm == "MBZP"), digits = 3)
```

95% confidence Intervals for the TE (Visit 1, Cytochrome p450 Pathway):

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)

setwd("/filepath/")

load("protect_output_cytochromep450_param_boot.Rdata")

summary.table <- rbind(subset(mbp.v1.out[[1]], param == "TE"),
                       subset(mibp.v1.out[[1]], param == "TE"),
                       subset(mbzp.v1.out[[1]], param == "TE"))
summary.table$method <- "Unconstrained"

save.table <- summary.table

summary.table <- rbind(subset(mbp.v1.out[[2]], param == "TE"),
                       subset(mibp.v1.out[[2]], param == "TE"),
                       subset(mbzp.v1.out[[2]], param == "TE"))
summary.table$method <- "MESSI (EB)"

save.table <- rbind(save.table, summary.table)

summary.table <- rbind(subset(mbp.v1.out[[3]], param == "TE"),
                       subset(mibp.v1.out[[3]], param == "TE"),
                       subset(mbzp.v1.out[[3]], param == "TE"))
summary.table$method <- "Discrete Selection"

save.table <- rbind(save.table, summary.table)

summary.table <- rbind(subset(mbp.v1.out[[4]], param == "TE"),
                       subset(mibp.v1.out[[4]], param == "TE"),
                       subset(mbzp.v1.out[[4]], param == "TE"))
summary.table$method <- "Hard Constraint"

save.table <- rbind(save.table, summary.table)
save.table$param <- "TE"
save.table$int.length <- save.table$ucl95 - save.table$lcl95

knitr::kable(save.table %>% filter(met.nm == "MBP"), digits = 3)

knitr::kable(save.table %>% filter(met.nm == "MIBP"), digits = 3)

knitr::kable(save.table %>% filter(met.nm == "MBZP"), digits = 3)
```

95% confidence Intervals for the NDE (Visit 2, Cytochrome p450 Pathway):

```{r, echo=FALSE, message=FALSE, warning=FALSE}
setwd("/filepath/")

load("protect_output_cytochromep450_param_boot.Rdata")

summary.table <- rbind(subset(mbp.v2.out[[1]], param == "NDE"),
                       subset(mibp.v2.out[[1]], param == "NDE"),
                       subset(mbzp.v2.out[[1]], param == "NDE"))
summary.table$method <- "Unconstrained"

save.table <- summary.table

summary.table <- rbind(subset(mbp.v2.out[[2]], param == "NDE"),
                       subset(mibp.v2.out[[2]], param == "NDE"),
                       subset(mbzp.v2.out[[2]], param == "NDE"))
summary.table$method <- "MESSI (EB)"

save.table <- rbind(save.table, summary.table)

summary.table <- rbind(subset(mbp.v2.out[[3]], param == "NDE"),
                       subset(mibp.v2.out[[3]], param == "NDE"),
                       subset(mbzp.v2.out[[3]], param == "NDE"))
summary.table$method <- "Discrete Selection"

save.table <- rbind(save.table, summary.table)

summary.table <- rbind(subset(mbp.v2.out[[4]], param == "NDE"),
                       subset(mibp.v2.out[[4]], param == "NDE"),
                       subset(mbzp.v2.out[[4]], param == "NDE"))
summary.table$method <- "Hard Constraint"

save.table <- rbind(save.table, summary.table)
save.table$param <- "DE"
save.table$int.length <- save.table$ucl95 - save.table$lcl95

knitr::kable(save.table %>% filter(met.nm == "MBP"), digits = 3)

knitr::kable(save.table %>% filter(met.nm == "MIBP"), digits = 3)

knitr::kable(save.table %>% filter(met.nm == "MBZP"), digits = 3)
```

95% confidence Intervals for the NIE (Visit 2, Cytochrome p450 Pathway):

```{r, echo=FALSE, message=FALSE, warning=FALSE}
setwd("/filepath/")

load("protect_output_cytochromep450_param_boot.Rdata")

summary.table <- rbind(subset(mbp.v2.out[[1]], param == "NIE"),
                       subset(mibp.v2.out[[1]], param == "NIE"),
                       subset(mbzp.v2.out[[1]], param == "NIE"))
summary.table$method <- "Unconstrained"

save.table <- summary.table

summary.table <- rbind(subset(mbp.v2.out[[2]], param == "NIE"),
                       subset(mibp.v2.out[[2]], param == "NIE"),
                       subset(mbzp.v2.out[[2]], param == "NIE"))
summary.table$method <- "MESSI (EB)"

save.table <- rbind(save.table, summary.table)

summary.table <- rbind(subset(mbp.v2.out[[3]], param == "NIE"),
                       subset(mibp.v2.out[[3]], param == "NIE"),
                       subset(mbzp.v2.out[[3]], param == "NIE"))
summary.table$method <- "Discrete Selection"

save.table <- rbind(save.table, summary.table)

summary.table <- rbind(subset(mbp.v2.out[[4]], param == "NIE"),
                       subset(mibp.v2.out[[4]], param == "NIE"),
                       subset(mbzp.v2.out[[4]], param == "NIE"))
summary.table$method <- "Hard Constraint"

save.table <- rbind(save.table, summary.table)
save.table$param <- "IE"
save.table$int.length <- save.table$ucl95 - save.table$lcl95

knitr::kable(save.table %>% filter(met.nm == "MBP"), digits = 3)

knitr::kable(save.table %>% filter(met.nm == "MIBP"), digits = 3)

knitr::kable(save.table %>% filter(met.nm == "MBZP"), digits = 3)
```

95% confidence Intervals for the TE (Visit 2, Cytochrome p450 Pathway):

```{r, echo=FALSE, message=FALSE, warning=FALSE}
setwd("/filepath/")

load("protect_output_cytochromep450_param_boot.Rdata")

summary.table <- rbind(subset(mbp.v2.out[[1]], param == "TE"),
                       subset(mibp.v2.out[[1]], param == "TE"),
                       subset(mbzp.v2.out[[1]], param == "TE"))
summary.table$method <- "Unconstrained"

save.table <- summary.table

summary.table <- rbind(subset(mbp.v2.out[[2]], param == "TE"),
                       subset(mibp.v2.out[[2]], param == "TE"),
                       subset(mbzp.v2.out[[2]], param == "TE"))
summary.table$method <- "MESSI (EB)"

save.table <- rbind(save.table, summary.table)

summary.table <- rbind(subset(mbp.v2.out[[3]], param == "TE"),
                       subset(mibp.v2.out[[3]], param == "TE"),
                       subset(mbzp.v2.out[[3]], param == "TE"))
summary.table$method <- "Discrete Selection"

save.table <- rbind(save.table, summary.table)

summary.table <- rbind(subset(mbp.v2.out[[4]], param == "TE"),
                       subset(mibp.v2.out[[4]], param == "TE"),
                       subset(mbzp.v2.out[[4]], param == "TE"))
summary.table$method <- "Hard Constraint"

save.table <- rbind(save.table, summary.table)
save.table$param <- "TE"
save.table$int.length <- save.table$ucl95 - save.table$lcl95

knitr::kable(save.table %>% filter(met.nm == "MBP"), digits = 3)

knitr::kable(save.table %>% filter(met.nm == "MIBP"), digits = 3)

knitr::kable(save.table %>% filter(met.nm == "MBZP"), digits = 3)
```
